Checkpoint 4

### 2020-05-01 Draft-Report.Rmd
update

---
title: "Draft Final Project"
author: "Sofia Pozsonyiova"
date: "4/30/2020"
output: html_document
---

@@

MAKE VISUAL FOR STATE COLOR

```{r}
ggplot(data = Finaldata, x = StateColor) + stat_count()
```

###Google TS

@@

###Final Data Set

>>>>

---
title: "Checkpoint 4"
author: "Quinn Rafferty, Sofia Pozsonyiova, Will Madairy, Federico Chung"
date: "4/24/2020"
output: 
  html_document:
    toc: true
    toc_float: true
---

@@

###Google TS
```{r}
Trump<- as.Date("03/16/2020", format = "%m/%d/%Y")
day1<-as.Date("03/10/2020",format = "%m/%d/%Y")
day2<-as.Date("03/24/2020",format = "%m/%d/%Y")

google_ts<-google%>%
  mutate(Day = as.Date(as.character(Day)))

a<-google_ts %>% 
  #filter(Day<=day2)%>%
  #filter(Day>=day1)%>%
  group_by(Region, Day) %>% 
  summarize(ChinaVirusSearch = median(ChinaVirusInterest)) %>% 
  ggplot(aes(x=Day, y=ChinaVirusSearch, color=Region))+
  geom_point()

ggplotly(a)
```

This plot shows the relationship of “China Virus” search interest over grouped by region. This plots shows that there are certainly key events that trigger an uptick in searches overall. In this plot it is not clear which region may search China Virus more or less often, but it does show a that the regions move together in search interest, which would imply federal level events like a Donald Trump tweet to trigger these interest spikes.

```{r}
b<- ggplot(Finaldata, aes(x = ChinaVirusInterest, fill = as.factor(State))) + 
  geom_density(alpha = 0.5)+ ggtitle("China Virus Density by State")

ggplotly(b)
```

We can see that the variability in Google interest in the term China Virus is has quite a large range between states. There are very few states that have high densities among the upper echelons of the interest scale but there are some interesting peaks of densities among the lower values. For example, we can see that Alaska, Wyoming and Iowa have unusal peaksaround the 25-50 range. It is is also interesitng interesting to note that there isn't an *obvious* mean or median value of China Virus interest among the states.

@@

```{r}
c <-  ggplot(Finaldata, aes(y=positive, x=Winner, fill=(Winner)))+
      geom_boxplot() +
      facet_wrap(~Region)+
      theme(legend.position = "none") +
      scale_fill_manual(values = c("Democrat"="blue3", "Republican"= "red3"))+
      lims(y= c(0,1000))+
      ggtitle("Positive COVID-19 Cases by State Political Party Winner & Region")
ggplotly(c)
```

(PUT DESCRIPTION)
\
\
